\documentclass[11pt]{exam}
\usepackage[margin=1in]{geometry}
\newcommand{\class}{Ancient Philosophy}
\newcommand{\term}{Phil 234}
\newcommand{\examnum}{Pop Quiz 1}
\newcommand{\examdate}{\date}
\newcommand{\timelimit}{10 Minutes}
\parindent 0ex

\begin{document}
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushright}
\begin{tabular}{p{2.8in} r l}
\textbf{\class} & \textbf{Name (Print):} & \makebox[2in]{\hrulefill}\\
\textbf{\term} &&\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} 
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}

\begin{minipage}[t]{3.7in}
\vspace{0pt}
\begin{itemize}
\item This quiz tests whether you are spending sufficient time on the assigned reading. If you fail, you will lose 2 of the 10 reading points allocated towards your final grade.
\item To pass the quiz, you must answer at least 5 questions correctly. 
\item Enter all requested information on the top of this page.
\item You may \textit{not} use your books, notes, etc.
\item Do not write in the table to the right.
\end{itemize}
 \rule[1ex]{\textwidth}{.1pt}

\end{minipage}
\hfill
\begin{minipage}[t]{2.3in}
\vspace{0pt}
%\cellwidth{3em}
\gradetablestretch{2}
\vqword{Problem}
\addpoints % required here by exam.cls, even though questions haven't started yet.	
\gradetable[v]%[pages]  % Use [pages] to have grading table by page instead of question

\end{minipage}
\begin{questions}
\addpoints
\question{Tick the correct answer:} 
\begin{parts}

\part[1] Socrates stands charged of…
\begin{checkboxes}
\choice Obstructing justice 
\choice Corrupting the youth 
\choice Murder
\choice None of the above
\end{checkboxes}


\part[1] What does Aristotle say in the Apology?
\begin{checkboxes}
\choice That socrates would never knowingly corrupt the Athenian youth
\choice Aristotle does not appear in the Apology
\choice That Socrates should not be put to death
\choice That some of the claims against Socrates are self-contradicting
\end{checkboxes}

\part[1] Which of the following is NOT true?
\begin{checkboxes}
\choice Socrates teaches students without being paid.
\choice Socrates claims to have no knowledge.
\choice Socrates considers himself wiser than many politicians, poets, and artisans.
\choice Socrates claims to know all things.
\end{checkboxes}
\part[1] Socrates claims that it would be absurd to knowingly corrupt the youth of Athens because...
\begin{checkboxes}
\choice the Athenian youth are too wise to be corrupted.
\choice the Athenian youth are protected by Athena.
\choice the Athenian youth are stubborn and impossible to persuade of anything.
\choice It would surround him with worse people, which could potentially cause him harm.
\end{checkboxes}

\part[1] After being condemned to death, what is Socrates' prophecy?
\begin{checkboxes}
\choice That Athens will decline after his death
\choice That there will never be anyone as wise as he is
\choice That after death he will be with heroes and wise people in Hades 
\choice That killing him will only bring more critics like him
\end{checkboxes}


\part[1] The Oracle at Delphi declared 
\begin{checkboxes}
\choice no one was more ignorant than Socrates 
\choice no one was smarter than Socrates 
\choice no one was wiser than Socrates 
\choice no one was a better philosopher than Socrates 
\end{checkboxes}


\part[1] At his trial, Socrates declares that
\begin{checkboxes}
\choice he will stop philosophizing 
\choice he will engage in Athenian politics
\choice he will not stop philosophizing  
\choice he will take care of his family 
\end{checkboxes}

\part[1] For Socrates, an unexamined life is a tragedy because it results in grievous harm to
\begin{checkboxes}
\choice the state  
\choice the justice system 
\choice the body  
\choice the soul 
\end{checkboxes}


  \part[1] At his trial, Socrates cross-examines
\begin{checkboxes}
\choice Anytus
\choice Plato
\choice Meletus 
\choice Crito 
\end{checkboxes}


\part[1] Which of the following does Socrates claim is not to be feared.
\begin{checkboxes}
\choice an unhealthy soul  
\choice death
\choice prosecution  
\choice imprisonment
\end{checkboxes}
\end{parts}


\end{questions}





\end{document}