\documentclass[]{article}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Long Essay 1},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\title{Long Essay 1}
\date{}

\begin{document}
\maketitle

\subsection{Long Essay 1}\label{long-essay-1}

\subsubsection{Prompt}\label{prompt}

In the \emph{Phaedo}, Socrates makes the following claim:

\begin{quote}
``the one aim of those who practice philosophy in the proper manner is
to practice for dying and death'' (64a3-4)
\end{quote}

In this paper, you will be examining Socrates' views on death. The paper
has two parts:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Why does Socrates believe that practicing philosophy is practicing for
  death? In answering this question, you must identify Socrates' views
  on the entities that philosophers must study and why he thinks that
  dying is conducive to that study. Do you think that Socrates is right
  that we cannot study these entities in this life? Why? Why not?
\item
  Socrate offers three arguments for our immortality from 69e-84b.
  (Ignore the fourth argument that comes later in the dialog.) Pick
  \textbf{one} of these arguments and explain it in detail. What is the
  weakest premise of this argument? Why? How might Socrates respond?
\end{enumerate}

\subsubsection{Further Instruction}\label{further-instruction}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Focus only on 57a--84b.
\item
  Read at least one of the articles listed below. Read more if you would
  find it useful.
\item
  This is a research essay. It must include proper citations and
  bibliography.
\item
  Write 1250-1500 words. No more. No less.
\item
  Submit your responses by Mon. 2/29/2016 @ 1pm.
\item
  I will check these submissions for plagiarism. If you use material,
  whether explicitly or implicitly, from any source, you must cite it.
\end{itemize}

\subsubsection{Further Resources}\label{further-resources}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{http://www.iep.utm.edu/phaedo/}{Entry in the \emph{Internet
  Encyclopedia of Philosophy}}
\item
  \href{/Teaching/Ancient/Assignments/Divided.pdf}{From the
  \emph{Phaedo} to the \emph{Republic}, Iakovos Vasiliou,} ch.1 of
  `Plato and the Divided Self'
\item
  \href{/Teaching/Ancient/Assignments/Two.pdf}{Philosophers and Death:
  Two Contrasting Arguments in Plato's \emph{Phaedo}, F.C. White}
\item
  \href{/Teaching/Ancient/Assignments/Degrees.pdf}{Degrees of Separation
  in the ``Phaedo'', Michael Pakaluk}
\end{itemize}

\end{document}
