\documentclass[10pt]{article}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Research Essay 1},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\title{Research Essay 1}
\date{}

\begin{document}
\maketitle

\subsubsection{Prompt}\label{prompt}

How might David Lewis use the existence of temporal parts to solve the
paradox of increase (also called the debtor's paradox)? What is the
biggest difficulty for this proposed solution? Can the difficulty be
overcome? Give reasons for your answer.

\subsubsection{Further Instruction}\label{further-instruction}

This essay covers material from Michael Rea's `Problem of Change' (on my
website) plus the following two readings from the reader:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Quine, `Identity, Ostension, and Hypostasis'
\item
  Lewis, `In Defense of Stages: Postscript B to ``Survival and
  Identity'''
\end{enumerate}

I have not supplied you with readings that deny the existence of
temporal parts. This is by design. For this essay, you must identify,
read, and use one scholarly article that presents an objection to Lewis.
Note that a scholarly article is not equivalent to an encyclopedia
entry, though you are welcome to use the encyclopedias listed on my
website to identify a scholarly article. A scholarly article is one that
is published in a peer reviewed journal like \emph{Mind}, \emph{The
Philosophical Review}, \emph{Nous}, \emph{Philosophical Studies}, etc.
You should begin your search by using \url{http://philpapers.org}. After
that, you will need to visit the library, or, at least, spend time using
the online library research tools.

\subsubsection{Word Count}\label{word-count}

1250--1500 words. Writing less than 1250 or more than 1500 words will
lose you points.

\subsubsection{Plagiarism}\label{plagiarism}

Please review the plagiarism policy on the syllabus. It is critical that
you prepare your assignment by yourself. I will be checking for
significant overlaps between submissions as well as checking answers
against Wikipedia, internet search results, standard essay sites, etc.
If you include material in your essay without citing it, you will
receive 0 for the assignment. A second violation will result in a 0 for
the course, a report to the Dean, and a petition for a note to be added
to your permanent academic record.

\subsubsection{Due Date}\label{due-date}

Please consult the syllabus and course website for the due date.

\subsubsection{Late Submissions}\label{late-submissions}

Per the policies outlined in the syllabus, late work will not be
accepted. As the policies also state, there are no make-ups. Any request
for special treatment will be ignored. If you foresee difficulties
submitting work on time, either because of personal or work commitments,
then you should start this paper early and submit it early.

\subsubsection{Format}\label{format}

Please submit your paper through Blackboard as a word file.

\subsubsection{Grading}\label{grading}

Please find the rubric and explanation of it
\href{/Teaching/Grading/}{here}.

\subsubsection{Resources}\label{resources}

Please find links to writing resources \href{/Teaching/Resources/}{here}

\end{document}
