\documentclass[12pt]{article}

\usepackage{fancyhdr}
 \pagestyle{fancy}
\lhead{ }

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\usepackage[usenames,dvipsnames]{color}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

\date{ \ }

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi


\begin{document}


\noindent\textbf{The Arrow Paradox}

\href{http://lowres-picturecabinet.com.s3-eu-west-1.amazonaws.com/39/main/2/14336.jpg}{http://lowres-picturecabinet.com.s3-eu-west-1.amazonaws.com/39/main/2/14336.jpg}

\section{Version 1}

\begin{enumerate}
\item If the arrow moves throughout the period of its flight, then it is moves at each instant of that period. 
\item The arrow occupies a space equal to its own volume at each instant. 
\item If the arrow occupies a space equal to its own volume at an instant, then it is not in motion at that instant. 
\item The arrow is not in motion at any instant of that period. (from 2-3)
\item The arrow does not move throughout the period of its flight. (from 4)
\end{enumerate}

\section{Version 2}

\begin{enumerate}
\item If the arrow moves throughout the period of its flight, then, when it moves, it moves in the present. 
\item The arrow is not in motion in the present. 
\item The arrow does not move throughout the period of its flight. 
\end{enumerate}
 
\section{The Static Account of Motion}

\begin{quote}
An object is in motion throughout a period if and only if the object occupies different positions at every instant of that period; it is in motion at an instant if and only if it occupies a different position at instants immediately before and after that instant. 
\end{quote}

\end{document}
