\documentclass[]{article}

\usepackage{fancyhdr}
 \pagestyle{fancy}
\rhead{\textsc{Scott O`Connor}}

\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\usepackage[usenames,dvipsnames]{color}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Check Sheet},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

\title{Check Sheet}
\author{Scott O’Connor}


% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}
\maketitle

\subsubsection{Check Sheet}\label{check-sheet}

Check these boxes before submitting your paper. This is for your benefit
only. Do not submit it to me.

\begin{longtable}[c]{@{}lc@{}}
\toprule
& Yes/No\tabularnewline
\midrule
\endhead
I understand that my paper will be graded according to a
\href{/Teaching/Grading/LongRubric.pdf}{rubric}, which I have read and
and understood. &\tabularnewline
I am not submitting my paper late and I have read the policies about
late submissions and make-ups on the syllabus. &\tabularnewline
My paper demonstrate a clear understanding of the prompt.
&\tabularnewline
My paper has addressed all the tasks listed under `tasks'.
&\tabularnewline
My paper uses the material from the assigned readings, notes, and
lectures. &\tabularnewline
My paper defends any view that the prompt requests me to defend
regardless of whether that is my view. &\tabularnewline
I have not either directly or indirectly used material from any source
without adequately indicating where I am doing so and citing that
source. &\tabularnewline
My paper is written in the requested style, e.g., essay, dialog, letter,
etc. &\tabularnewline
My paper contains the required number of words. &\tabularnewline
I have carefully proof read my paper. &\tabularnewline
My paper is in either docx, rtf, or pdf format. &\tabularnewline
\bottomrule
\end{longtable}

\end{document}
