\documentclass[article,oneside]{memoir}
\usepackage{unicode-math}
\usepackage{graphicx,url}
\usepackage{rotating} 
\usepackage{memoir-article-styles} 
\usepackage{fontspec} 
\usepackage{xunicode} 
\usepackage[polutonikogreek,english]{babel}
\newcommand{\greek}[1]{{\selectlanguage{polutonikogreek}#1}}
\def\myaffiliation{Metaphysics: Phil 205}
\def\myauthor{Scott O'Connor}
\def\myemail{\small{\texttt{\href{mailto:soconnor@njcu.edu}{soconnor@njcu.edu}}}}
\def\mytitle{Phenomenalism}
\def\mykeywords{2015, 2016}
\usepackage[usenames,dvipsnames]{color}                     
\usepackage[xetex, 
	colorlinks=true,
	urlcolor=BlueViolet, % external links
       citecolor=BlueViolet, % citations
        filecolor=BlueViolet, % local files
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
 	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}   



\usepackage{setspace}



\begin{document}
\setromanfont[Mapping=tex-text]{Minion Pro} 
\setsansfont[Mapping=tex-text]{Myriad Pro}  
\setmonofont[Mapping=tex-text,Scale=MatchLowercase]{Minion Pro} 
\setkeys{Gin}{width=1\textwidth} 
\chapterstyle{article-3}  
\pagestyle{kjh}

\title{\mytitle}

\author{\myauthor \\
 \emph{\myaffiliation \\ }}
%\thanks{OMITTED}
%\published{\footnotesize Draft. Please do not cite without permission.}


\maketitle

\section{Introduction}

Things must be a certain way for us to have any experiences of them. For instance, things must have color and shape for us to see them, they must be spatially separated from us and other things if we are distinguish them from one another and from ourselves, etc. Let us call the features and relations that things must have for us to perceive them \emph{phenomenal properties}. Metaphysicians have been interested in the following question: 
\begin{itemize}
\item Do we experience things  \emph{because} they have phenomenal properties, or do things have phenomenal properties \emph{because} we experience them?
\item Compare: Is piety good \emph{because} God loves it, or does God love piety \emph{because} it is good? 
\end{itemize} 
We shall call \emph{phenomenalists} those who believe that things have phenomenal properties because we experience them.  It is a view that Aristotle attributes to Protagoras: 
\begin{quotation}
...all things believed [ta dokounta panta] and [all] appearances [ta phainomena] are true’ (1009a8).
\end{quotation}
`The things that appear to us' (ta phainomena) are things as they appear to our senses, i.e. the contents of our sense perceptions. The `things that we believe’ (ta dokounta) are general things as we believe them to be, i.e. the contents of our beliefs in general. We can believe things that we do not sense and \emph{vice versa} 

\begin{description}
\item[Phenomenalism (PHEN):] Anything that appears thus and so to someone, and anything that someone believes to be thus and so, is thus and so (i.e. all appearances and all beliefs are true).
\end{description}
Distinguish the following two claims:


\begin{enumerate}
\item For \emph{some} property F, an object O is F because O appears F to someone. 
\item For \emph{any} property F,  an object O is F because O appears F to someone. 
\end{enumerate}
The first claims says that objects have just some properties because of how they appear to us. The second claims that any property an object has is explained by how it appears to us. PHEN makes the second claim. The schematic argument for PHEN:
\begin{itemize}
\item P1. No object has an essence.  
\item P2. If no object has an essence, then we cannot speak and think about things. 
\item P3. But we can speak and think about things. 
\item P4. We can speak and think about things if they have an essence because of how they appear to us (even if they have no essence independently of how they appear to us.) 
\item C. Therefore, things have an essence because of how they appear to us.  
\end{itemize}

\section{P1. Essence}

The word `essence'  is from the Latin word `essentia', which was coined to translate a phrase invented by Aristotle, `to ti en einai.' This roughly translates as `what it was for something to be'. He introduced it to describe the stable natures that changing being have over time. The phrase was then extended to discuss the natures of non-changing beings. For our purposes, we will define \emph{essentialism} as the conjunction of the following two claims:
\begin{itemize}
\item Each thing belongs to some kind K such that if that thing ceases to be a K, it will cease to exist...e.g., Socrates dies if he ceases to be human, Flipper dies if he ceases to be a dolphin. 
\item For every kind K, there are a unique set of individually necessary conditions that are jointly sufficient for membership of that kind, e.g., being rational and being an animal are each necessary conditions for being human. They are also jointly sufficient for being a human; anything that satisfies both is a human and nothing is a human that does not satisfy both. 
\end{itemize}
Some standard objections to essentialism: 

\begin{enumerate}
\item It is possible for objects to change kinds without ceasing to exist, e.g., Lot's wife, some fish, werewolves, etc.
\item There are no necessary and sufficient conditions for kind membership, e.g., species evolve, amputees are still members of their kind, etc.
\item Belief is essentialism leads to prejudices. 
\item Things change always and in every way, and nothing is constant about them.
\end{enumerate}

\section{P2. Essence and thought/language}
\begin{quotation}
For not to signify one thing [a unitary thing, a determinate thing] amounts to not signifying anything at all. (Aristotle)
\end{quotation}


\begin{enumerate}
\item To think and speak about something is to think and speak about one thing as opposed to another, e.g., to think and speak about Socrates is to think and speak about Socrates as opposed to something else. 
\item  In order to think and speak about one thing as opposed to another, we must be able to indicate what distinguishes the thing that we are thinking and speaking about from other things, e.g., to think and speak about a cloud we must be able to indicate what distinguishes the cloud from other things.  
\item It is in virtue of a thing having an essence that is the very thing that it is, as opposed to any other thing.
\item So, in order to distinguish the thing that we are thinking and speaking about from other things, we must be able to indiciate its essence. 
\item[C] If an object does not have an essence, then we cannot think and speak about it. 
\end{enumerate}

This is above all because it was crucial in the defence that we can think and speak about a thing, x, only if x has an essence; for it is in virtue of having an essence that this thing, x, is the very thing that it is, as opposed to any other thing.

\noindent \emph{Moral: thought and language about things is possible only if they have essences, e.g., I can think and speak about x only if there is some essence E such that x is E.}


\section{P3. Language and thought are possible}

Aristotle thinks it is obvious that language and thought is possible. But, proving that it is possible is tricky. He writes the following: 

\begin{quotations}
If he [the disputant] says nothing [i.e. if he really accepts that language is impossible], it is ridiculous to try to say something against one who does not have a statement to make about anything, in so far as he is like that; for such a person is to that extent already like a vegetable (1006a13–15).
\end{quotation}

Aristotle is offering a self-refutation argument, namely, he is claiming that anyone who denies the possiblity of thought and language refutes themselves. 

\begin{enumerate}
\item Suppose that S denies that thought and language are possible. 
\item All denials involve thought and language. 
\item Thus, S thinks and speaks when she denies that thought and language are possible. 
\item Therefore, S cannot consistently deny that thought and language are possible. 
\end[enumerate}

\noindent \emph{NB: this argument does not prove that thought and language are possible. It proves only that you cannot consistently deny that it possible.]

\section{P4. Essences as they appear to us}

Distinguish two claims: 
\begin{itemize}
\item Socrates has an essence in virtue of himself. 
\item Socrates has an essence in virtue of how he appears to us. 
\end{itemize}

Suppose that Socrates is essentially human. Our first claim says that he is human, as opposed to a giraffe, dolphin, or hedgehog, not because of his relation to anything else. He is a human precisely because of himself. Our second claims agrees that Socrates is essentially human. But it states that it is precisely in virtue of how he appears to us that Socrates is human; his being human is explained by how he appears to us and not explained by how he is independently of his relationship to aything else. 

Here, then, is a simple way of presenting our argument for Phenomenalism: 

\begin{enumerate}
\item Language and thought about things is possible. 
\item Language and thought about things is possible only if things have an essence. 
\item Things do not have an essence in virtue of themselves. 
\item So, things must have an essence in virtue of how they appears to. 
\end{enumerate}





\end{document}
