\documentclass[oneside]{article}
%\usepackage[scale=0.70]{geometry}
\usepackage{footnote}
\makesavenoteenv{tabular}

\usepackage{mdwlist}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenx}
\usepackage[T1]{fontenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Ethics Minor Requirements}
\chead{}
\rhead{ }
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\rmdefault}{ppl}
\renewcommand{\rmdefault}{ppl}
\usepackage{setspace}
\usepackage{multirow}



\begin{document}
\renewcommand*\rmdefault{ppl}\normalfont\upshape

\title{Minor Program in Ethics \\ \emph{Degree Requirements} }
\maketitle

\section*{Catalog Description}
A Minor in Ethics offers students the opportunity to complement their academic Major with the study of ethical theories and their application in diverse areas of human endeavor. It is an interdisciplinary course of study that draws upon faculty and courses from many departments. While the Philosophy \& Religion Department provides the theoretical foundations of the study of ethics and some of its applications, such as in environmental ethics or bioethics, courses from participating departments add a variety of application areas. It is the aim of the program to prepare students from all possible disciplines for their professional lives, not only enabling them to deal with ethical questions and challenges in a reflective and theoretically grounded manner, but also to provide some of the tools needed to participate in professional ethics bodies.
\section*{Credit Requirements--18 total}

\begin{center}
    \begin{tabular}{ | l | p{4cm}| p{4cm} |}
    \hline
     Type & Credits  & Notes \\ \hline
     \textbf{Year I} & & \\ \hline
Required & 3 credits &  PHIL 207  \\ \hline
Restricted Elective & 6 credits &   PHIL 125, PHIL 113, WGST  110, PHIL 112, PHIL 231, PHIL 245, PHIL 246 \\ \hline 
\textbf{Year II} & & \\ \hline
Restricted Elective & 9 credits & PHIL 244,  PHIL 230, PHIL 239, SECU 224, BUSI 321, SOCI 336, SOCI 341, NURS 406, PHIL 408, PHIL 510, ACCT 510, BUSI 612, ACCT 770 \\ \hline
\end{tabular}
\end{center}

\section*{Notes}

\begin{description}
\item[General Education:] Only two General Education courses can be selected for the requirements of the Minor. Marked with * below. 
\item[Gen. Ed. vs. Gen. Studies:] NJCU transitioned to a new General Education Program in Fall 2015. Students who enrolled in NJCU before that date were participating in the General Studies Program, whose courses have been replaced. Please consult an advisor in the Philosophy/Religion Department on how to substitute courses from one program for the other.  
\item[Prerequisites:] Successfully completing ENGL 101 is a prerequisite for all Philosophy \& Religion courses at the 200 level or above that are \emph{not} part of the General Education program. Courses from other departments may have different prerequisites. Consult the relevant department. 
\end{description}

\section*{Courses}
\begin{center}
    \begin{tabular}{ | l | p{6.5cm}| p{1.78cm}|}
\hline
\multicolumn{5}{ |l| }{\textbf{Year I}} & \textbf{Course} & \textbf{Number} \\ \hline
\multirow{1}{*}{Required} & Ethics  & PHIL 207 \\ \hline 


 \multirow{8}{*}{Restricted Electives}   & Environmental Ethics & PHIL 113* \\
 &  Ethics in Everyday Life & PHIL 125* \\
  &  Bioethics and Technology & PHIL 112 \\
 & Contemporary Moral Issues & PHIL 103*\\
  & Philosophy of War and Peace & PHIL 231* \\
     & Social Justice& PHIL 245* \\
 & Food, Philosophy \& Global Health & PHIL 246* \\
& Diversity \& Difference & WGST 110* \\ \hline
\multirow{1}{*}{\textbf{Year II}} & \textbf{Course} & \textbf{Number} \\ \hline
 \multirow{13}{*}{Restricted Electives} & Philosophy of Law & PHIL 230 \\
    & On Evil &  PHIL 239\\  
        & Political and Social Philosophy & PHIL 244 \\
   & Independent Study in Philosophy & PHIL 408\\
   & Ethics, Values, and Society & PHIL 510 \\
   & Business Ethics & ACCT 510 \\
   & Ethical and Professional Standards for Investment Management & ACCT 770 \\
   & Ethics, Responsibility and Global Issues & BUSI 321 \\
   & Behavioral Issues and Ethics in Management & BUSI 612 \\
   & Healthcare Law and Ethics (\textbf{2 cr.}) &   NURS 406 \\
   & Ethics in Professional Security Studies & SECU 224 \\
   &  Professional and Ethical Responsibilities for Substance Abuse Counselors & SOCI 336 \\
   & Law and Social Value & SOCI 341 \\ \hline
\end{tabular}
\end{center}



\end{document}
