% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = xelatex

\documentclass[11pt]{article}
\usepackage{fontspec}
\defaultfontfeatures{Mapping=tex-text}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{verbatim}
\usepackage[margin= 1 in]{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{letterpaper} % or letter or a5paper or ... etc
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent 
\usepackage{mathrsfs}
\usepackage{bbding}
\usepackage[usenames,dvipsnames]{color}
\usepackage{natbib}
\usepackage{stmaryrd}
%\usepackage{mathpartir}
\usepackage{txfonts}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{fontspec}
%\setmainfont{Hoefler Text}
\setmainfont[BoldFont={Minion Pro Bold}]{Minion Pro}
\usepackage{hyperref}
\usepackage{lastpage, fancyhdr}
%\usepackage{setspace}
\pagestyle{fancy}
\lhead{}
\chead{Scott O'Connor\\Ancient Philosophy} 
\rhead{}
\lfoot{}
\cfoot{\thepage\space of \pageref{LastPage}} 
\rfoot{}
\footskip=30 pt
\headsep=25pt
\thispagestyle{empty}
\hypersetup{colorlinks=true, linkcolor=Sepia, urlcolor=Sepia, citecolor=BrickRed}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}


\usepackage{covington}
\usepackage{fixltx2e}
\usepackage{graphicx}
\begin{document}

%\maketitle
\thispagestyle{empty}
\begin{center} \LARGE{Ancient Philosophy\\ \emph{De Anima}}\\ \vspace*{2mm}
\large{Scott O'Connor}\end{center}
\thispagestyle{empty}\vspace*{3mm}
\vspace*{-8mm}

\section*{Aristotle's potentiality / actuality distinction}

\noindent Central to A's metaphysics is a distinction between potential beings and actual beings. Being potentially a house and being actually a house; being potentially a dog and being actually a dog; being potentially seeing and being actually seeing.\\

\noindent A does not think that facts about potential beings can be reduced to facts solely about actual beings. For example: he does not think that the fact that a collection of bricks constitutes a potential house can be reduced solely to facts about bricks.\\

\noindent Rather, a being (or collection of beings) X is (are) a potential \emph{F} if and only if there is a single process such that, as a result of undergoing that process, X is actually \emph{F}. For example, a collection of bricks constitute a potential house because there is a single process, namely an exercise of the art of housebuilding, that it can undergo such that it becomes an actual house.\\

\noindent A's general account of soul employs a tiered notion of the potentiality / actuality distinction. The example A gives is the difference between someone who can acquire knowledge (because, say, they are a normally developed human being at the appropriate age) / a person who has actually acquired knowledge (say of French) / and a person who is employing that knowledge (say by speaking French). The first person is in a state of ``first potentiality'' / the second in a state of ``second potentiality'' and ``first actuality'' / the third in a state of ``second actuality''.

\section*{The general account of soul}

\noindent In Bk. 2, Ch. 1 A offers a general definition that covers all souls. Such a definition, while it will be true of all souls, will not be particularly informative, and so he also proceeds, in Chs. 4 and following, to discuss the various kinds of soul in more detail. \\

\noindent At the beginning of Ch. 1, A tells us that the soul is a particular kind of nature, namely the form of a living organism; thus, the relation of body--soul an instance of the more general form--matter relationship.\\

\noindent The soul is a second potentiality / first actuality of a certain kind of body. The kind of body at question is ``organic'' (composed of organs), i.e. one's whose parts are capable of functioning in integrated ways. For example, the leaves, roots, stem etc., of plants are capable of functioning in various integrated ways.\\

\noindent Thus, A's general account of soul: the first actuality of a natural body that is potentially alive. In other words, the soul just is the integrated set of abilities the possession of which makes a living organism the kind of organism it is.\\

\noindent This means that A does \emph{not} distinguish between the various kinds of activities human beings engage in and attribute a subset of them to the soul and a subset to something else (such as the body). But, it does \emph{not} mean that A can't make distinctions between various activities human beings can perform when such a distinction is relevant (e.g. he can think that the purely automatic maintenance of the body isn't relevant for Ethics or practical philosophy).\\

\noindent A thinks this renders the question ``are the soul and body one'' easily answerable: of course they are different, since form and matter are different; but, since the presence of soul makes the body the kind of body it is, you can't have that kind of body without it being ensouled

\section*{Homonymy}

\noindent A's general account of homonymy: A and B are ``homonyms'' iff the same name ``N'' applies to both A and B but the reason why it applies is different. For example, the eye of a living organism and the eye of a statue are ``homonyms'' because the same name applies to them (i.e. ``eye'') but the reason why that name applies is different for each. For the eye of a living organism, it applies because it has the power of sight; for the eye of the statue it applies because it ``looks like'' or ``resembles'' the eye of a living organism in shape and location.\\

\noindent So, for A, a body that lacks the ability to perform the activities characteristic of an X (e.g. a dog, cat, human being) can only be the body of an X homonymously

\section*{Integrated abilities}

\noindent The ability to perform the activities of nutrition can be had without the abilities to perceive and think (e.g. in plants); the ability to perceive can be had without the ability to think but \emph{not} without the ability to nourish; the ability to think requires all the others (at least for earthly organisms).\\

\noindent As noted above, A thinks that there can be a general definition of soul as such (given above), but that general account is not that informative. In part, this is because the possession of higher-order abilities ``colors'' or ``affects'' the lower-order abilities of the organism. For example, possessing the ability to think means that the human beings ability to nourish itself is quite different from, say, plants or animals ability to nourish itself.\\

\noindent This is part of the reason why A thinks that virtue (and ethics generally) is something that only human beings can possess; it isn't just that we possess the ability to think; its because our possessing that ability means we can perform the lower-order abilities in a manner not available to non-human animals.

\section*{The soul as \emph{aitia}}

\noindent In Ch. 4 A says that the soul is the \emph{aitia} in three ways of the organism whose soul it is: as source of motion, what it is for, and substance (i.e. form)
\begin{itemize}
\item Efficient \emph{aitia} of the locomotion, growth, and alteration of the organism

\item Formal \emph{aitia} of the organism (i.e. it makes the organism the kind of organism it is)

\item Final \emph{aitia} of the organism's ``body'' (i.e. its parts are for the sake of performing those abilities)
\end{itemize}

\end{document}
