\documentclass[11pt]{exam}
\usepackage[margin=1in]{geometry}
\newcommand{\class}{Time}
\newcommand{\term}{Hon 202}
\newcommand{\examnum}{Pop Quiz 2}
\newcommand{\examdate}{\date}
\newcommand{\timelimit}{10 Minutes}
\parindent 0ex

\begin{document}
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushright}
\begin{tabular}{p{2.8in} r l}
\textbf{\class} & \textbf{Name (Print):} & \makebox[2in]{\hrulefill}\\
\textbf{\term} &&\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} 
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}

\begin{minipage}[t]{3.7in}
\vspace{0pt}
\begin{itemize}
\item This quiz tests whether you are spending sufficient time on the assigned reading. If you fail, you will lose 2 of the 10 reading points allocated towards your final grade.
\item A pass requires 5 correct answers.  
\item Enter all requested information on the top of this page.
\item You may \textit{not} use your books, notes, etc.
\item Do not write in the table to the right.
\end{itemize}
 \rule[1ex]{\textwidth}{.1pt}

\end{minipage}
\hfill
\begin{minipage}[t]{2.3in}
\vspace{0pt}
%\cellwidth{3em}
\gradetablestretch{2}
\vqword{Problem}
\addpoints % required here by exam.cls, even though questions haven't started yet.	
\gradetable[v]%[pages]  % Use [pages] to have grading table by page instead of question

\end{minipage}
\begin{questions}
\addpoints
\question{Tick the correct answer:} 
\begin{parts}

\part[1] Which of the following scientific notions is NOT mentioned in ch.12:
\begin{checkboxes}
\choice Entropy 
\choice Magnetism
\end{checkboxes}


\part[1] Ch.12 is concerned with Zeno's paradoxes of motion
\begin{checkboxes}
\choice True
\choice False
\end{checkboxes}

\part[1] Ch.12 uses which of the following two weapons to discuss time? 
\begin{checkboxes}
\choice Javelins
\choice Arrows
\end{checkboxes}



\part[1] The relation `being earlier than' is
\begin{checkboxes}
\choice symmetrical 
\choice assymetrical
\end{checkboxes}

\part[1] Time has a direction but not an order
\begin{checkboxes}
\choice True
\choice False
\end{checkboxes}

\part[1] If A is among the causes of B, then A is earlier than B
\begin{checkboxes}
\choice True
\choice False
\end{checkboxes}

\part[1] Which famous author is mentioned in ch.12?
\begin{checkboxes}
\item J.R.R Tolkien
\item H.G. Wells
\end{checkboxes}

\part[1] Ch.12 asks whether time could run backwards? 
\begin{checkboxes}
\item True
\item False
\end{checkboxes}

\part[1] Ch.12 talks about mind, memory, and experience?
\begin{checkboxes}
\item True
\item False
\end{checkboxes}

\part[1] Ch.12 talks about alien perceptions of time?
\begin{checkboxes}
\item True
\item False
\end{checkboxes}

\end{parts}


\vspace{3.5in}




\end{questions}





\end{document}