\documentclass[oneside]{article}
 \headheight = 25pt
\footskip = 20pt
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\renewcommand{\rmdefault}{ppl}
\usepackage{fancyhdr}
 \pagestyle{fancy}
 \lhead{\textbf{\textsc{\small Scott O'Connor\\Ancient Philosophy}}}
 \chead{}
 \rhead{\large\textbf{\textsc{Independent Project---Literature Review}}}
 \lfoot{\footnotesize{\thepage}}
 \cfoot{}
 \rfoot{\footnotesize{\today}}
 \usepackage{longtable,booktabs}
\tolerance=700



\begin{document}
\thispagestyle{fancy}

\subsection*{Requirements}\label{independent-project-stage-2}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Literature Review--see below
\item
  Due Date: 04/09/2018 at midnight through Blackboard
\item Time Commitment: expect to spend up to 8--12 hours on this phase over the next month. Start early!
\item
  Word Count: 750-1000 words divided fairly equally between the sections
  described below.
\item
  Citations and bibliography required.
\end{itemize}

\subsection*{Introduction}\label{introduction}

You have decided on a question.  Now what? You need to identify some articles and
books that seem relevant to your question. But how do you use these resources to find
your answer? Do you need to read them in detail? Do you need to
summarize each in detail? No! That's way too much work. Look at the
bibliography at the end of any scholarly paper or the back of any book.
The bibliography likely amounts to hundreds if not thousands of pages of
work. But the author didn't write in detail about all of this work. What
gives?

The purpose of this assignment is to teach you to collect relevant material and then do something with all the
material . What's it for? What should you include? How
much work do you really have to do on it all? That means---literature
review time!

\subsubsection{What is a literature
review?}\label{what-is-a-literature-review}

Let's start with an analogy. You've been asked to design a website to
help renters find homes in Jersey City. To make it easier for renters,
you've been asked to identify some criteria that would allow them narrow
their searches. What should these search criteria be? In order to answer
this question, you need to read several different rental adverts. What
are the common types of information that comes up? Obviously, price,
location, size, square footage, etc. But what about a dishwasher? What
about the color of the walls, carpet type, proximity to cinemas? Users
of the website will be overwhelmed by too many criteria, so you need to
decide what's most useful for them.

Writing a literature review is similar in two ways:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Your job in writing a literature review is to identify relevant
  similarities and dissimilarities in the various resources that seem to
  address your topic. You will regularly find that different parts of
  the literature take opposing sides on your question. Here we have an
  important trend that you want to mention. You will also find common or
  dominant reasons for various answers. Again, this is something you
  want to note and write about.
\item
  The person developing the website doesn't tell you the best house to
  live in. They group together the most important features that renters
  might look for. Similarly, literature reviews don't take a stand on
  the issues. They try to present the various dominant/common views
  about an issue as neutrally as possible.
\end{enumerate}

What about all the nitty gritty details? Do you have to write in length
about them? Probably not. Suppose you would like to know why students
pick one university over another. You conduct an interview of 1000
students. You may find that cost, reputation, location, etc., are common
responses. Let us also imagine that you collect detailed information
about each student, about how much they can afford, their price
tolerance, etc. Do you need to include these details of the 1000
students into your study? Of course not! Your job is to extrapolate from
the details and report what's common.

Does that mean that no detail is required? No. Literature reviews often
include a discussion of some representative resource. Think of our
previous example. Suppose you discover that students weigh the cost of
their education heavily when deciding what school to attend. Don't tell
me about each of the 1000 students. But it helps to talk in detail about
one or two students who really illustrate the general discovery that you
have made.

Similarly, literature reviews will both explain some of the current,
common views about a topic \emph{and} discuss a couple of resources to
illustrate these common features/trends.

\subsubsection{The Process--Don't submit this
part!}\label{the-processdont-submit-this-part}

Here are some general approaches to writing a literature review. Best
practice may vary by discipline:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Create an annotation for each item in your bibliography. Don't worry
  about reading the item in full. Often reading abstracts,
  introductions, and conclusions will suffice. Skim a relevant chapter
  in a book, not the whole book. Your goal is to identify the relevance
  it has to your main question.
\item
  Write a couple of sentences stating how your source answers your
  question. Write another couple of sentences outlining the main reason
  for its answer. Note some interesting details and examples. One or two
  nice quotes is also helpful. Keep account of the page numbers.
\item
  Look at your annotations. Identify themes and common claims. Group the
  items into different categories. For instance, you might notice that
  there are two diverging answers to your question. You might also
  notice that there are some agreements on why to answer the question
  one way rather than the other.
\item
  Write down the common themes, arguments, you see in your annotations.
  Try describe these commonalities as clearly as possible.
\item
  Choose some representative works, e.g., maybe there is a particularly
  strong article that argues for one answer and a different one that
  argues for a different answer.
\item
  Read your representative works in detail. Take detailed notes as you
  do so.
\end{enumerate}

\subsubsection{Writing the Literature Review--Do Submit this
Part!}\label{writing-the-literature-reviewdo-submit-this-part}

The structure of literatures review will vary by disciplines and
questions. However, since the main goal of this exercise is to teach you
how to do research, I want you to write the following three sections.
The first raises a question. The second offers one answer. The third
offers a different answer. Both the second and third sections outline
the reasons for their respective answers and include some details from a
representative resource defending that answer.

This structure is artificial. Many questions admit of more than two
answers. Many similar answers have subtle differences. That's ok! If you
can identify and explain two different mains answers to your question,
then you will have learned the skill this assignment is designed to
teach.

\subsubsection{Section 1: Context}\label{section-1-context}

Suppose you pick up a paper and it begins `Students choose college based
on either cost alone or reputation alone.' That's a bit abrupt. The
author does not explain why it's important to identify why students pick
college over another, nor do they explain why anyone would be interested
in reading about the issue. Now consider this opening:

\begin{quote}
New Jersey's high schools are full and getting fuller. We are graduating
more and more of these students too. Not only that, more and more of our
graduates are going on to attend college. So, New Jersey seems to be
doing well by its young folk. Unfortunately, though, this good news is
tempered by a worrying trend. Fewer and fewer or our students are
attending college in New Jersey itself. Our young people are leaving in
great numbers to attend colleges and universities in other states. This
bodes poorly for the future. It's unclear that they will return to
benefit the state they left. Why is this happening? Why are young people
choosing to attend college out of state? There are two opposing views.
One group of researchers argue that cost alone is the culprit. They
claim that our young people are leaving because colleges and
universities in other states are cheaper. Not everyone agrees. A
different group of researchers blame the exodus on students' belief in
the respective qualities of in-state and out of state colleges. The
researchers offer very different remedies to the proposal. If the former
is correct, then we should focus on lowering tuition in the Garden
State. If the latter is correct, we need to do a better job at marketing
the strengths and successes of our state institutions.
\end{quote}

Notice that this introduction does three things. First, it establishes a
shared context, i.e., it informs the reader about some phenomenon.
Second, it raises a question or problem about the phenomenon. Third, it
clearly states the answer and explains the answer's importance.

Your literature review needs to begin in this way too. Provide some
context. Write a paragraph or two. Raise a problem. State two different
solutions. Explain the importance of the problem and solutions.

\subsubsection{Section 2: Answer 1}\label{section-2-answer-1}

Here you will explain one way your question is answered in the
literature. Your job here is to summarize the answer given and also the
main reasons offered for that answer. You will also write a few
paragraphs summarizing some details from a representative work that
takes this line.

\subsubsection{Section 3: Answer 2}\label{section-3-answer-2}

Here you will explain a different way that your question is answered in
the literature. Your job here is to summarize the answer given and also
the main reasons offered for that answer. You will also write a coupe of
paragraphs summarizing some details from a representative work that
takes this line.

\end{document}
