\documentclass[oneside]{article}
 \headheight = 25pt
\footskip = 20pt
\usepackage[T1]{fontenc}
\renewcommand{\rmdefault}{ppl}
\usepackage{fancyhdr}
 \usepackage{fancyhdr}
 \pagestyle{fancy}
 \lhead{\textbf{\textsc{\small Scott O'Connor}}}
 \chead{}
 \rhead{\small{\textsc{Peer Review}}}
 \lfoot{\footnotesize{\thepage}}
 \cfoot{}
 \rfoot{\footnotesize{\today}}
\tolerance=700

\begin{document}
\thispagestyle{fancy}

\addtocounter{section}{1}

\subsection{Paper Topic} 
\begin{enumerate}
\item Write one sentence that clearly describes the main point of the document.   
\item Is that main point clearly stated in the introductory paragraph? 
\item Does the entire paper argue for that one main point?  Or does it argue for something else?  Explain.
\end{enumerate}

\subsection{Paper Structure}

\begin{enumerate}
\item Are the sections of the paper clear? Are there section headings? If not, what should they be and where should they be included? 
\item As you read the paper, do you question, ``What is the author doing now?''  ``What's going on?'', or could you follow the paper easily?  How could the flow of the paper be improved?  Explain.
\item For each paragraph, write one sentence that summarizes the point made in that paragraph. 
\item Do any paragraphs make more than one point? Should those paragraphs be divided in two?
\item  Could any of the paragraphs be consolidated into one? 
\item  Could any paragraph be cut?   
\end{enumerate}

\subsection{Sentence Structure}  
\begin{enumerate}
\item Underline any phrases or full sentences that are awkward or confusing. Suggest revisions.
\item Underline the beginning and end of each sentence. Do the sentences flow naturally into one another? Could any improvements be made? 
\item Underline the topic of each sentence. Does it clearly relate to the main point of the paragraph that contains it? 
\item Identify any redundant phrases. Suggest more concise ways of phrasing the points.  
\end{enumerate}



\subsection{Exposition} 
\begin{enumerate}
\item Do you think the author has misunderstood anything about the topic? 
\item Would an intelligent person who has never read about the topic easily understand the paper? If not, what extra information should the author provide?  Be specific.
\item  Are there any phrases or sentences that might confuse a reader? Should extra explanation be provided or should those phrases/sentences be cut? 
\end{enumerate}


 
\subsection{Critical Engagement}
\begin{enumerate}
\item  Identify and describe the argumentative strategy in your own words (1-2 sentences).
\item How effectively does the author execute this strategy?  Did you work hard to figure out what they are doing?  Did you follow along up to a point and then lose track?  Where did you get lost?  Be specific.
\item Does the author argue for their claims or do they just state their claims without explaining or justifying them?  Be specific. 
\item  Should anything be added to the argument?  Explain.
\end{enumerate}

\subsection{Academic Integrity}
\begin{enumerate}
\item Are there excessively long quotes, i.e., longer than 30 words? 
\item Does the author use quotes without explaining the material themselves, i.e., are they using quotes to avoid writing the paper themselves?
\item Are quotations clearly marked with quotation marks and/or block quotes? 
\item Is there a works cited page? If so, is full information provided? Are the entries formatted correctly? 
\item Are in-line citations accurately formatted? 
\item Are there any phrases or sentences that are written in a very different style from the rest of the paper? If so, search those phrases/sentences online? Are they quotations from wikipedia, a published source, some other website? Help your peer avoid plagiarism by clearly indicating questionable material. 
\end{enumerate}



\end{document}

