\documentclass[]{article}
%\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Essay},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\title{Essay}
\date{}

\begin{document}
\maketitle

This assignment concerns
\href{/Teaching/Examined/Ethics/Kirinyaga.pdf}{`Kirinyaga', ch.~1, by
Mike Resnik}

\subsection{Introduction}\label{introduction}

Koriba strangles a newborn child. He claims that the traditions of his
people, the Kikuyu, say it is morally required of him to do so.
Maintenance is concerned. They send Barbara Eaton to investigate.

\subsection{Purpose}\label{purpose}

The purpose of this assignment is to help you practice the following
skills that are essential to your success in this course and others.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Charitably explaining arguments about issues of public importance.
\item
  Understanding that there are different cultural norm and how those
  norms guide different behavior.
\item
  Explaining difficult concepts in your own words.
\end{enumerate}

\subsection{Task}\label{task}

In this assignment, pretend to be Barbara Eaton and write a report that
does the following:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Describes conditions on the ground. What did you see? Did people seem
  happy, healthy, etc?
\item
  How did people respond to you? Were they welcoming? Were they hostile?
  What did they say to you?
\item
  How did Koriba explain his strangling of the child?
\item
  How did Koriba respond when you claimed it was immoral to kill the
  child?
\end{enumerate}

\subsection{Word Count}\label{word-count}

500-750. Essays shorter than 500 words or longer than 750 words will
lose points.

\subsection{Due Date}\label{due-date}

Please consult the syllabus and course website for the due date.

\subsection{Late Submissions}\label{late-submissions}

Per the policies outlined in the syllabus, late work will not be
accepted. Any request for special treatment will be ignored. If you
foresee difficulties submitting work on time, either because of personal
or work commitments, then you should start this paper early and submit
it early.

\subsection{Plagiarism}\label{plagiarism}

Please review the plagiarism policy on the syllabus. It is critical that
you prepare your assignment by yourself. Use only the textbook and
handouts---it will take you less time to work through these materials
than to find and read other sources. I will be checking for significant
overlaps between submission as well as checking answers against
Wikipedia, internet search results, standard essay sites, etc. If you
include material in your essay without citing it, you will receive 0 for
the assignment. A second violation will result in a 0 for the course, a
report to the Dean, and a petition for a note to be added to your
permanent academic record.

\subsection{Format}\label{format}

Please submit the file as a Microsoft Word file through Blackboard.

\subsection{Grading}\label{grading}

Please find the rubric and explanation of it
\href{/Teaching/Grading/}{here}.

\subsection{Resources}\label{resources}

Please find links to writing resources \href{/Teaching/Resources/}{here}

\end{document}
