\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\title{Alternative NYC Assignment}
\begin{document}
\maketitle

\subsection*{General Instructions}
\begin{itemize}
\item  Write  a minimum of 750 words for each day's activity. 
\item Take at least two photographs per day. Include the photographs in your submission. 
\item Your submission can be a blog, a word document, etc. Submit it to me via email. 
\item Complete these assignments by August, 31st. 
\end{itemize}

\subsection*{Day 1: Metropolitan  Museum  of  Art,  Greek  exhibition}
Greek  art  tells  us  how  the  Greeks  saw  themselves.  What  do  you  think  they  want  to  communicate  about  being  Greek  with  this  art?  

\subsection*{Day  2: Astoria,  NY}
Read  something  about  Astoria before you start: \url{https://macaulay.cuny.edu/eportfolios/berger2011/astoria/brazil-in-astoria/athens-in-astoria/}\\

Begin your tour at the Athens  Square  Park.  After documenting  the  park, explore Astoria thoroughly. I  want  you  to  document  the  influence  of  Ancient  Greece  in  this  neighborhood.  Where  and  how  is  that  influence  evident?  How  do  you  think  contemporary  Greek  immigrants  related  to  their  ancient  heritage?  What  values  did  they  aspire  to  and  what  did  they  want  to  communicate  when  celebrating  their  heritage  in  sculpture,  architecture,  etc.?  Make  sure  to  eat  some  Greek  food  and  tell  me  about  it.    



\subsection*{Day  3:  Architecture in NY}

Begin  at  the  World  Trade  Center  and  walk  to  Wall  Street,  then  walk  to  City  Hall,  the  Supreme  Court,  etc.  I  want  you  to  document  the  best  examples  of  Greek  influence  in  the  architecture  you  see.  Pay  special  note  of  the  civic  buildings.  Also  look  up  high.  After  identifying  Greek  influence,  I  want  you  to  write  about  why  the  architects  would  have  incorporated  these  elements  in  the  way  they  did.  What  were  they  trying  to  communicate  by  doing  so? 

\subsection*{Day  4: Hall  of  Fame  for  Great  Americans  at  Bronx  Community  College}

Find  info here:  \url{www.bcc.cuny.edu/halloffame/}\\ 

Greek  elements  are  used  in  this  celebration  of  Americans at this Hall of Fame.  I  want  you  to  reflect  on  what  the  venue  and  statues  are  intended  to  communicate  about  America  and  the  relevant  people  depicted.  What  particular  values  are  being  celebrated?  I  want  you  to  also  think  about  why  they  used  Greek  elements  in  this  construction.    

\subsection*{Day  5:  You  decide}  

Suppose  I  were  to  develop  this  assignment  for  other  students.  How  might  I  do  so?  Identify  some  place  you  have  yet  to  visit  (it  could  be  a  different  part  of  Astoria),  or  some  buildings,  or  some  activity  in  New  York  that  clearly  connects  New  York  city  to  Ancient  Greece.  Obviously,  you  should  visit  and  document  the  area.    Your  job:  convince  me  that  this  place  would  be  a  good  fit  for  this  type  of  alternative  assignment.   

\end{document}